Paper_stuff

### 2023-09-29 Paper_stuff.Rmd
JT PLOTS: Its gonna be ME

summary(Mothership_post$Treatment_Responder)
summary(Mothership_post$Anx_Responder)
summary(Mothership_post$Dep_Responder)

@@

>>>>

@@

```{r}
devtools::install_github("AWKruijt/JT-RCI")
library(JTRCI)

# generate some random data:
df <- cbind.data.frame("ppid" = seq(1:64), 
                       "pre" = rnorm(64, 65, 8), 
                       "post" = c(rnorm(32, 40, 8), rnorm(32, 45, 8)),
                       "group" = rep(c("treatment", "control"), each = 32))

# The function will determine which criterion to use based on the available information 
# f.i. when no (healthy or dysfunctional) norm values are provided, the function will  
# return criterion A using the baseline distribution as the 'dysfunctional distribution':

JTRCI(data = df, 
      ppid = "ppid", 
      pre = "pre", 
      post = "post",  
      reliability = .8, 
      indextype = "JT", 
      JTcrit = "auto")

df

Mothership_post$ID1
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post))

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post))

RCI_df_dep <- data.frame(RCI_df_dep)
RCI_df_anx <- data.frame(RCI_df_anx)

JTRCI (data = RCI_df_anx, 
       pre = "pre", 
       post = "post", 
       ppid = "ID1", 
       reliability = .9, 
       indextype = "JT", 
       JTcrit = 20,
       group = "Disorder",
       facetplot = T,
       plottitle = "Anxeity: JT indices by disorder")

JTRCI(data = df, pre = "pre", post = "post",  group = "group", ppid = "ppid",
      reliability = .8, indextype = "JT", JTcrit = "C",
       normM = 30, normSD = 5, dysfM = 60, dysfSD = 5, 
      facetplot = T, plottitle = "JT indices by group:")
```
